Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-17 paper/paper.tex
updated referee reply
explain random forest results

The observed flux for the \lya line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$
which gives a \lya/H$\beta$ flux ratio of
4.9$\pm$0.1 \citep{Izotov04}.
Comparing the \lya/H$\beta$ ratio with the theoretical
expectation from case B recombination of $23.3$ \citep{Hummer1987} one
can estimate an escape fraction of $20$\% for \lya radiation.

@@

Figure \ref{fig:tree} shows as an illustration the results for a
single classification tree.
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
This means that these 3 parameters are the most useful parameters
in finding models with low $\chi^2/d.o.f.$.

The results of the random forest classifier yield that the clump outflow velocity
$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
that the \lya emission comes from the clumps $P_{\rm cl}$, are the
most influential parameters in finding a model with low
$\chi^2/d.o.f.$.

>>>>

The observed flux for the \lya line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$
which gives a \lya/H$\beta$ flux ratio of
4.9$\pm$0.1 \citep{Izotov04}.
Comparing the \lya/H$\beta$ ratio with the theoretical
expectation from case B recombination of $23.3$ \citep{Hummer1987} one
can estimate an escape fraction of $20$\% for \lya radiation.
Figure \ref{fig:results} shows \tol's \lya\ profile reported by
\cite{mashesse03}. This measurement as mede with the Space Telescope
Imaging Spectrograph on board the Hubble Space Telescope, these
observations have a spectral resolution of $\sim 37$\kms\ at the
\lya\ wavelength.

@@

Figure \ref{fig:tree} shows as an example the results for a
single classification tree.
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
In this example the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.

The results of the random forest classifier over $500$ trees yield
that the clump outflow velocity $v_{\infty,\rm{cl}}$, the clump
velocity dispersion $\sigma_{\rm cl}$ and the probability that the
\lya emission comes from the clumps $P_{\rm cl}$, are the most
influential parameters in finding a model with low $\chi^2/d.o.f.$.
